Title

### 2023-03-25 Cap2.tex
Actualización 2

\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many different one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state.
\end{itemize}

>>>>

\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state.
\end{itemize}

### 2023-03-25 Cap3.tex
Actualización 2

\section{OPR Circuits}
\begin{itemize}
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} The theorem gives the general form that the operator of an OPR circuit can have. \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{align*}
U = (\vec{v}_0, \vec{v}_1, \cdots, \vec{v}_{2^n-1})
\end{align*}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\end{itemize}

>>>>

\section{OPR Circuits}
\begin{itemize}
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{align*}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{align*}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\end{itemize}

### 2023-03-25 Cap5.tex
Actualización 2

\section{Exponential maps $e^{iHt}$}
\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation.
\item Consider operations $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Theorem:} A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.
\item \textbf{Examples:} Every matrix $H$ for one qubit, any $n$-qubit pauli matrix, some sums of Pauli matrices, etc.
\end{itemize}

>>>>

\section{Exponential maps $e^{iHt}$}
\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
\item \textbf{Examples.} Some examples are: Every matrix $H$ for one qubit, any $n$-qubit pauli matrix, some sums of Pauli matrices, etc.
\end{itemize}
